---
output: github_document
language: en
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# `financr`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/financr)](https://CRAN.R-project.org/package=financr)
[![Codecov test coverage](https://codecov.io/gh/Clement-LVD/financr/graph/badge.svg)](https://app.codecov.io/gh/Clement-LVD/financr)
[![R-CMD-check](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

![ ](https://img.shields.io/badge/Package-bold?style=flat&logoColor=black&logoSize=2&label=R&labelColor=black&color=green)

Retrieves financial data from Yahoo Finance. Get historical or latest values of financial assets or currencies exchanges rates, latest insights, assets association (related to each other), etc.

Functions are divided into three main families:

- 'search_': Search for assets using free-text queries
- 'get_': Retrieve financial values and insights, given symbols
- 'last_': Get market summaries, latest values of major assets, world-level indices, currencies and cryptocurrencies

See the [vignette 'Summary of financr Functions'](https://clement-lvd.github.io/financr/articles/Functions_summary.html).
          
## Installation

You can install the development version of financr:

``` r
devtools::install_github("clement-LVD/financr")
```

## Examples

More examples on [the example Vignette](https://clement-lvd.github.io/financr/articles/example.html).

**Get ticker symbol from free-texts.** Given keyword(s) such as companies names, search symbols with `search_assets()`.

```{r example1}
library(financr)

indices <- search_assets(c("Dow jones"
                           , "euronext")
                         , type = "index" )

str(indices)
```


Optionally use the '`get_values`' parameter to add latest prices to these results.

```{r example-scraping}
indices2 <- search_assets(
  c("Dow jones", "euronext")
  , type = "index"
  , get_values = TRUE )

str(indices2)
```

Exploring the results of `search_assets()` is a way to find the symbol of an asset. `search_assets_quick()` is a variant.

**Get historical financial data.**  Given ticker symbol(s), get historical financial data with `financr::get_historic()`. Default interval is daily values.

```{r example2}
histo <- get_historic(
  c("SAAB-B.ST", "VOLV-B.ST")
  , .verbose = FALSE)

str(histo)

```

 
## Vignettes

- [Summary of financr functions](https://clement-lvd.github.io/financr/articles/Functions_summary.html).


- [The 'last_ family' of functions](https://clement-lvd.github.io/financr/articles/last_family.html).

- [Currency-related functions](https://clement-lvd.github.io/financr/articles/currencies.html).
 

**Yahoo Finance API Licence.** This package retrieves data from Yahoo Finance, a property of Yahoo Inc. Users must comply with [Yahoo Finance's API terms](https://legal.yahoo.com/us/en/yahoo/terms/product-atos/apiforydn/index.html). See more informations on the [legal Vignette](https://clement-lvd.github.io/financr/articles/About_the_Yahoo_Finance_License.html).
