---
output: github_document
language: en
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
Sys.setlocale("LC_TIME", "en_US.UTF-8")  # En anglais

```

# `financr`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/financr)](https://CRAN.R-project.org/package=financr)
[![Codecov test coverage](https://codecov.io/gh/Clement-LVD/financr/graph/badge.svg)](https://app.codecov.io/gh/Clement-LVD/financr)
[![R-CMD-check](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

![ ](https://img.shields.io/badge/Package-bold?style=flat&logoColor=black&logoSize=2&label=R&labelColor=black&color=green)

`'financr'` retrieves financial data from Yahoo Finance : 

- Historic of financial data, e.g., market prices, currency exchange rates.
- Latest insights on financial assets such as companies, major indices, currencies and cryptocurrency exchange rates.
- Other insights, e.g., validity of financial symbol(s) and other assets associated with these symbol(s).

See the [vignette 'Summary of financr Functions'](https://clement-lvd.github.io/financr/articles/Functions_summary.html).
          
## Installation

You can install the development version of financr:

``` r
devtools::install_github("clement-LVD/financr")
```

## Examples

**Get ticker symbol from free-texts.** Given keyword(s) such as companies names, search financial ticker symbols with `financr::search_assets()`.

```{r example1}
library(financr)

indices <- search_assets(c("Dow jones", "euronext"), type = "index" )

str(indices)
```


Or use `financr::search_summary()`, in order to add latest prices to the results of the previous example.

```{r example-scraping}
swed_indices <- search_summary( c("SAAB", "VOLVO"), exchange = "STO")

str(swed_indices)
```

If you don't know the ticker symbol of an asset, exploring the results of `financr::search_summary()`, `search_assets()` or `search_assets_quick()` is a way to find it.

**Get historical financial data.**  Given ticker symbol(s), get historic of financial values with `financr::get_historic()` :

```{r example2}

# Fetch historical values, given ticker symbol(s)
histo <- get_historic(c("SAAB-B.ST", "VOLV-B.ST"), .verbose = FALSE)
# Default interval is daily values.

str(histo)

```


 
## Vignettes [WIP]
**Get latest financial insights with the 'last_' family of functions**, e.g., latest values and insights about major indices, world-indices and crypto-currencies. See the [vignette on the '`last_` family' of functions`](https://clement-lvd.github.io/financr/articles/last_family.html).

**Change currencies at current exchange rates and get historic of exchange rates.** See the [vignette on currency-related functions](https://clement-lvd.github.io/financr/articles/Get_changes.html).
 
**Cascading functionnality.** `'financr'` offer the possibility to chain these process, e.g.,

1. get ticker symbol and latest insights from keyword(s) such as company names, 
2. then get the financial historic associated with these ticker symbol, 
3. and finally convert their values in a given standardized currency, e.g., 'USD'.

See the vignette on [`search_summary()` and `get_historic()`](https://clement-lvd.github.io/financr/articles/get_info_and_historic.html).

## Licence
This package retrieves data from Yahoo Finance, a property of Yahoo Inc. Users must comply with [Yahoo Finance's API terms](https://legal.yahoo.com/us/en/yahoo/terms/product-atos/apiforydn/index.html). See more informations on the [legal Vignette](https://clement-lvd.github.io/financr/articles/About_the_Yahoo_Finance_License.html).
