---
output: github_document
language: en
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
Sys.setlocale("LC_TIME", "en_US.UTF-8")  # En anglais

```

# '`financr`'

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/financr)](https://CRAN.R-project.org/package=financr)
<!-- badges: end -->

![ ](https://img.shields.io/badge/Package-bold?style=flat&logoColor=black&logoSize=2&label=R&labelColor=black&color=green)

`'financr'` retrieves financial data from Yahoo Finance.

- Get historical market data (e.g., market prices, currencies exchange rates) ; 
- Get latest insights on companies, financial symbols, major indices, currencies and crypto-currencies exchanges rates ;
- Convert currencies and crypto-currencies with latest exchange rates.

See the [Vignette 'Summary of financr Functions'](https://clement-lvd.github.io/financr/articles/Functions_summary.html).
          
## Installation

You can install the development version of financr:

``` r
devtools::install_github("clement-LVD/financr")
```

## Examples

**Get ticker symbol and actual values.** Given keyword(s) such as companies names, search latest stock values with `financr::get_info_from_name()`.

```{r example}
library(financr)

swed_indices <- get_info_from_name(names = c("SAAB", "VOLVO"))

str(swed_indices) # Results of the day, over all marketplaces
```

If you don't know the ticker symbol of a financial value, exploring the results of `financr::get_info_from_name()` is a way to find it.

**Get historical financial data.**  Given ticker symbol(s), get historic of financial values with `financr::get_historic()` :

```{r example2}

# Fetch historical values, given ticker symbol(s)
histo <- get_historic(symbols = c("SAAB-B.ST", "VOLV-B.ST"), .verbose = FALSE)

str(histo)

```

Each lines of this `data.frame` are daily values.

 
## Vignettes

**Change currencies at current exchange rates and get historic of exchange rates.** See the Vignette of [`get_changes()` and `get_currencies()`](https://clement-lvd.github.io/financr/articles/Get_changes.html).
 
**Get latest financial values and insights on major world-indices and crypto-currencies.** See the [vignette of `get_indices()` and `get_crypto()`](https://clement-lvd.github.io/financr/articles/get_indices_and_get_crypto.html).
 
**Cascading functionnality.** `'financr'` offer the possibility to chain these process, e.g.,

1. get ticker symbol and latest insights from keyword(s) such as company names, 
2. then get the financial historic associated with these ticker symbol, 
3. and finally convert their values in a given standardized currency, e.g., 'USD'.

See the vignette on [`get_info_from_names()` and `get_historic()`](https://clement-lvd.github.io/financr/articles/get_info_and_historic.html).

## Licence
This package retrieves data from Yahoo Finance, a property of Yahoo Inc. Users must comply with [Yahoo Finance's API terms](https://legal.yahoo.com/us/en/yahoo/terms/product-atos/apiforydn/index.html). See more informations on the [legal Vignette](https://clement-lvd.github.io/financr/articles/About_the_Yahoo_Finance_License.html).
