---
output: github_document
language: en
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# `financr`

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/financr)](https://CRAN.R-project.org/package=financr)
[![Codecov test coverage](https://codecov.io/gh/Clement-LVD/financr/graph/badge.svg)](https://app.codecov.io/gh/Clement-LVD/financr)
[![R-CMD-check](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

![ ](https://img.shields.io/badge/Package-bold?style=flat&logoColor=black&logoSize=2&label=R&labelColor=black&color=green)

Retrieves financial data from Yahoo Finance : 

- Historical market data, e.g., prices of assets, currencies exchange rates.
- Latest insights on assets, e.g., major indices, currencies and cryptocurrencies.
- Other insights, e.g.,  market summary, assets association (related to each other), symbol validation.

See the [vignette 'Summary of financr Functions'](https://clement-lvd.github.io/financr/articles/Functions_summary.html).
          
## Installation

You can install the development version of financr:

``` r
devtools::install_github("clement-LVD/financr")
```

## Examples

**Get ticker symbol from free-texts.** Given keyword(s) such as companies names, search symbols with `financr::search_assets()`.

```{r example1}
library(financr)

indices <- search_assets(c("Dow jones", "euronext"), type = "index" )

str(indices)
```


Optionally use `add_latest_values` parameter to add latest prices to these results.

```{r example-scraping}
indices2 <- search_assets(c("Dow jones", "euronext"), type = "index", add_latest_values = TRUE )

str(indices2)
```

If you don't know the ticker symbol of an asset, exploring the results of `search_assets()` or `search_assets_quick()` is a way to find it.

**Get historical financial data.**  Given ticker symbol(s), get historic of financial values with `financr::get_historic()` (default interval is daily values).

```{r example2}
histo <- get_historic(c("SAAB-B.ST", "VOLV-B.ST"), .verbose = FALSE)

str(histo)

```

 
## Vignettes

- [Summary of financr functions](https://clement-lvd.github.io/financr/articles/Functions_summary.html).

- [The '`last_` family' of functions`](https://clement-lvd.github.io/financr/articles/last_family.html).

- [Currency-related functions](https://clement-lvd.github.io/financr/articles/currencies.html).
 
- [Workflow example](https://clement-lvd.github.io/financr/articles/get_info_and_historic.html).

**Yahoo Finance API Licence.** This package retrieves data from Yahoo Finance, a property of Yahoo Inc. Users must comply with [Yahoo Finance's API terms](https://legal.yahoo.com/us/en/yahoo/terms/product-atos/apiforydn/index.html). See more informations on the [legal Vignette](https://clement-lvd.github.io/financr/articles/About_the_Yahoo_Finance_License.html).
