---
output: github_document
language: en
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
Sys.setlocale("LC_TIME", "en_US.UTF-8")  # En anglais

```

# '`financr`'

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

[![CRAN status](https://www.r-pkg.org/badges/version/financr)](https://CRAN.R-project.org/package=financr)
[![Codecov test coverage](https://codecov.io/gh/Clement-LVD/financr/graph/badge.svg)](https://app.codecov.io/gh/Clement-LVD/financr)
[![R-CMD-check](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Clement-LVD/financr/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

![ ](https://img.shields.io/badge/Package-bold?style=flat&logoColor=black&logoSize=2&label=R&labelColor=black&color=green)

`'financr'` retrieves financial data from Yahoo Finance.

- Get historical market data (e.g., market prices, currencies exchange rates)
- Get latest insights on financial assets such as companies, major indices, currencies and crypto-currencies exchanges rates
- And other helper functions, such as converting currencies and cryptocurrencies using the latest exchange rates.

See the [Vignette 'Summary of financr Functions'](https://clement-lvd.github.io/financr/articles/Functions_summary.html).
          
## Installation

You can install the development version of financr:

``` r
devtools::install_github("clement-LVD/financr")
```

## Examples

**Get ticker symbol from free-texts.** Given keyword(s) such as companies names, search financial ticker symbols with `financr::search_from_text()`.

```{r example1}
library(financr)

indices <- search_from_text(texts = c("Dow jones", "euronext"), type = "index" )

str(indices) # Ticker symbols of index (all exchange places)
```


Or retrieve the symbols and latest values on the stocks exchange places with `financr::get_info_from_name()`.

```{r example-scraping}
swed_indices <- get_info_from_name(names = c("SAAB", "VOLVO"), exchange = "STO")

str(swed_indices) # More or less similar than the previous example + latest values of the day
```

If you don't know the ticker symbol of an asset, exploring the results of `financr::get_info_from_name()` or `search_from_text()` is a way to find it.

**Get historical financial data.**  Given ticker symbol(s), get historic of financial values with `financr::get_historic()` :

```{r example2}

# Fetch historical values, given ticker symbol(s)
histo <- get_historic(symbols = c("SAAB-B.ST", "VOLV-B.ST"), .verbose = FALSE)
# Default interval is daily values.

str(histo)

```


 
## Vignettes

**Change currencies at current exchange rates and get historic of exchange rates.** See the Vignette of [`get_changes()` and `get_currencies()`](https://clement-lvd.github.io/financr/articles/Get_changes.html).
 
**Get latest financial values and insights on major world-indices and crypto-currencies.** See the [vignette of `get_indices()` and `get_crypto()`](https://clement-lvd.github.io/financr/articles/get_indices_and_get_crypto.html).
 
**Cascading functionnality.** `'financr'` offer the possibility to chain these process, e.g.,

1. get ticker symbol and latest insights from keyword(s) such as company names, 
2. then get the financial historic associated with these ticker symbol, 
3. and finally convert their values in a given standardized currency, e.g., 'USD'.

See the vignette on [`get_info_from_names()` and `get_historic()`](https://clement-lvd.github.io/financr/articles/get_info_and_historic.html).

## Licence
This package retrieves data from Yahoo Finance, a property of Yahoo Inc. Users must comply with [Yahoo Finance's API terms](https://legal.yahoo.com/us/en/yahoo/terms/product-atos/apiforydn/index.html). See more informations on the [legal Vignette](https://clement-lvd.github.io/financr/articles/About_the_Yahoo_Finance_License.html).
