---
title: "Currency-related functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Currency-related functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette presents methods for working with currency exchange rates.

#### get_changes() & get_changes_historic() 

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

- `get_changes()` fetch the latest exchange rate, given currencies symbols :

```{r changes}
library(financr)

changes <- get_changes(from = c("RON", "USD"), to = "EUR")

changes[ , c("from", "to",  "regularmarketprice", "currency", "timestamp")]

```


- Or get the historic of exchange rates, given currencies symbols : 

```{r change-historic}

changes <- get_changes_historic(from = c("EUR", "RON") )

str(changes)

```

Currencies are indicated with the same syntax across `get_changes_historic()` and `get_changes()`, and both are converting to 'USD' by default. E.g., pass a named list of character vectors, or two separate lists of equal length.


```{r change-ways}
df2_days <- get_changes_historic(from = c("EUR" = "RON", "USD" = "EUR"))
 
same_as_df2_days <- get_changes_historic(from = c("EUR", "USD"), to =c("RON" , "EUR"))

```

**Range and Interval Parameters.** Default is 1 row per day for a 1-year period if no '`interval`' and '`range`' parameters are indicated. E.g., retrieve one observation per month over a five-year period.

```{r change-ranges}
df_month <- get_changes_historic(
  from = c("EUR", "JPY")
  , interval = "1mo", range = '5y')

str(df_month)
```

---

### last_currencies()

Get a `data.frame` of currencies symbols and names.

```{r currencies}
currencies <- last_currencies()
str(currencies)
```

It is helpful to understand the currency symbols used by the Yahoo Finance API, such as those found in the currency column of the `data.frame` returned by `get_historic()`.
 
**Parameters.** 

- Add the latest market values ('USD') for each currency with '`add_usd_values`' parameter,

- And/or filter symbols with the '`keep`' parameter (case insensitive). Hereafter we filter out the results with a regular expression.

```{r currencies2}
few_currencies <- last_currencies(keep = c("R.N",  "^Z")
                                  , get_changes = T )
few_currencies
```

