---
title: "Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette show a workflow example, relying on the Yahoo Finance API.

**Search for ticker symbols, given keyword(s).** E.g., search symbols of all index with 'Dow jones' or 'Euronext' (case insensitive).

```{r setup}
library(financr)
indices <- search_assets(texts = c("Dow jones", "euronext"), type = "index" )
str(indices)
```

---

**Search for symbols and latest prices on the exchange places, given keyword(s).** E.g., search the symbols of 'Volvo car' and 'Saab' in the Stockholm exchange place (case insensitive).

```{r example-price}
swedish <- search_assets(c("Volvo car", "Saab")
                         , exchange = "STO"
                         , get_values = T)
str(swedish)

```

---

**Get historical financial data, given symbols of assets.** Get historical values, given ticker symbol(s), see below.

```{r example3}
historic <- get_historic(symbols = swedish$symbol)

str(historic)
```

Additional attributes indicates such as the symbols of currencies in the `data.frame`, e.g., attributes of the `'historic'` `data.frame` from the previous example indicates that prices are in the 'SEK' currency. 

---

**Get names of currencies.** And optionally add insights from `get_changes()`, e.g., latest market prices of the currency ('USD').
 
```{r}
unknown_currencies <- unique(historic$currency)

values_currencies <- last_currencies(keep = unknown_currencies, get_changes = T)

head(values_currencies)

```

