---
title: "Summary of Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summary of Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
This vignette explains the functions offered by `'financr'`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## Overview

**Source.** Yahoo Finance is used consistently as a data source across the package.

**Inputs.** Each function expects a specific type of input, based on its prefix.

```{r inputs, echo = F}

knitr::kable(
data.frame(Prefix = c("search_", "get_", "last_")
, Example  = c("`search_assets('Saab')`", "`get_historic('^DJI')`", "`last_indices()`"  )
, Expected_input = c("Free-text(s)"
, "Financial symbol(s) such as a ticker symbol^[https://en.wikipedia.org/wiki/Ticker_symbol] (e.g., 'AAPL') or ISO 3-letter currency code^[https://en.wikipedia.org/wiki/ISO_4217] (e.g., 'USD')"
, "Do not require any input. All arguments are optional"                                
                                )     

) )

```

---

**Outputs.** All the `'financr'` functions return a standardized `data.frame`, see the last section ['Return Conventions'](#return-conventions).

Functions with the `'_historic'` suffix return an historic of financial data, while the others retrieve latest financial data.

---

## Details


**search_ family.**
        
```{r search-fn, echo=FALSE}

fn <- data.frame(Example =   c( 
"`search_assets('Saab', get_values = T)`"
                     
 ,"`search_assets('Saab')`" 
 
 ,"`search_assets_quick('Saab')`" ) 
  
 
 , Data.frame_returned =  c(  "Assets names, ticker symbols, latest insights and financial values" 
                        ,"Assets names and symbol(s) associated with the texts searched"   
                       ,"Assets names and symbol(s) associated with the text searched" )
          
)
colnames(fn) <- c("Example", "Returned `data.frame`")

knitr::kable(fn,   
               , format = "pipe"
             , caption = "Functions with the prefix `'search_'` retrieve latest data and expect free-text input(s)."    , font_size = 10) 
             
        
```

- Source : Yahoo Finance API (https://query2.finance.yahoo.com) 

---

**get_ family.**

```{r get-fn, echo = F}

fn <- data.frame(Example = c( "`get_historic('SDV1.F')` <br> & `get_historic_light('SDV1.F')`"
                             , "`get_values('SDV1.F')`"
                  , "`get_similar('SDV1.F')`"
  
                  , "`get_changes('USD', 'EUR')`",  "`get_changes_historic('USD', 'EUR')`" 
                 
                  ) 
  
  , Input = c("Asset symbol(s), such as ticker symbols"
   , "Asset symbol(s)"
,"Asset symbol(s)"
 ,"ISO currency code(s)"
 ,"ISO currency code(s)"
  )

 , Data.frame_returned =  c(  "**Historic** of financial data"
 ,"**Latest** insights and financial values"
 , "**Latest** symbols associated with those provided and similarity scores"
 ,"**Latest** exchanges rates" , "**Historic** of exchanges rates"
                           )
)

colnames(fn) <- c("Example", 'Input',"Returned `data.frame`")


knitr::kable(fn,   
               , format = "pipe"
             , caption = "Functions with the prefix `'get_'` retrieve the historical or latest financial values, given financial symbol(s)"    , font_size = 10) 

```

- Source : Yahoo Finance API (https://query2.finance.yahoo.com) 

---

**last_ family.**

```{r fn, echo=FALSE}

last_fn <- data.frame(
  Example = c( "`last_market_summary()`",
                     "`last_indices()`" 
               , "`last_currencies()`", "`last_crypto()`" 
                        
                      )
 , data.frame_returned =  c( "Latest summary information for a set of major financial market indices*",
   "World indices latest insights and values (USD)^‡^"
    ,   "ISO currency codes for currencies, names and (optionally) latest values* (USD)"
   , "100 major crypto-currencies latest insights and values (USD)^‡^"   )
  )

knitr::kable(last_fn
             
             , caption = "Functions with the prefix `'last_'` retrieve latest data and do not require any input (all arguments are optional).")

```

- \* : Retrieve latest data from Yahoo Finance API (https://query2.finance.yahoo.com) 

- ‡ : Scraping latest data from Yahoo Finance pages, i.e. https://finance.yahoo.com/markets/world-indices/ or [...]/markets/crypto


See the vignette of the 'last_' functions.

`vignette("last_family", package = "financr")`

---

**Other function.**

```{r other-fn, echo = F}

knitr::kable(data.frame(Example  =  '`valid_symbol("SAABF")`'
        ,    Input =  "Text(s) to verify" 
          , Data.frame_returned = "(logical values) Validity of financial symbol(s)"
             ) 
        , caption = "Other helper functions")

```

- Source : Yahoo Finance API (https://query2.finance.yahoo.com) 

---

## Return Conventions
Regarding a `data.frame` returned by `'financr'` functions, the column names are:

- following the 'snake_case' conventions^[https://wikipedia.org/wiki/Snake_case], e.g., in lowercase and without spaces;
- and symbols are replaced (e.g., "%' is replaced by 'percent').
