---
title: "Summary of financr Functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Summary of financr Functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette explains the functions offered by `'financr'`.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

```

## `'financr'` Overview

- **All the `'financr'` functions return a standardized `data.frame`.**
    - Functions with the `'_historic'` suffix return an historic of financial data, 
    - while the others retrieve up-to-date data and latest financial insights.

```{r fn, echo=FALSE}
fn <- data.frame(Minimal_example = c(
                     "`get_indices()`" , "`get_crypto()`"   ,"`get_info_from_name('Saab')`"

  , "`get_historic('AAPL')`"
                 
                  , "`get_changes('USD', 'EUR')`",  "`get_changes_historic('USD', 'EUR')`" 
                  ,'`valid_symbol("AAPL")`'
                  ) 
  , Input = c( "", "", "Free-texts, e.g., companies names" 

,"Ticker symbol(s)^[https://en.wikipedia.org/wiki/Ticker_symbol]"
, "Currencies to convert"
 , "Currencies + optional `range` and `interval`"
, "Text(s) to verify"
                             )
             , Data.frame_returned =  c( "World indices, latest insights and values"
                        , "100 major crypto-currencies, latest insights and values (USD)"
                        ,"Ticker symbol(s) associated with the text, latest insights and values" 

 , "**Historic** of financial data"
 ,"Latest exchanges rates" , "**Historic** of exchanges rates"
 , "Validity of financial symbol(s)"
                           )
             , Data = c( rep("Latest**^‡^**", 2),"Latest**^†^**", "Historic*",  "Latest**^‡^**", "Historic*", "Latest*")
          
)
colnames(fn) <- c("Example", "Input", "Returned `data.frame`", "Data")

knitr::kable(fn,   
               , format = "pipe"
             , caption = "Table 1. Overview of `'financr'` Functions"    , font_size = 10) 
             
          
  # column_spec(1, width = "4em")%>% 
  # column_spec(2, width = "11em")

```

Sources :

- \* : Yahoo Finance APIs, e.g., query1.finance.yahoo.com/v1/finance/currencies ; [...]/v8/finance/chart or query2.finance.yahoo.com/v6/finance, etc.
- **†** : Scraping from https://finance.yahoo.com/lookup/  
- **‡** : Scraping from other Yahoo Finance pages, such as https://finance.yahoo.com/markets/world-indices/ or [...]/markets/crypto, etc.

---

**Standardized Return Conventions.** Regarding all the `data.frame` returned by `'financr'` functions:
    
The column names are:

- following the ['snake_case' conventions](https://wikipedia.org/wiki/Snake_case), e.g., in lowercase and without spaces;
- and symbols are replaced (e.g., "%' is replaced by 'percent');

Regarding the values : 

- Numeric values are returned as `integer` or `numeric` class of values. 

---

## `'financr'` Specifics 

**Role of financr in the 'Reach Yahoo Finance' ecosystem.** `'financr'` only retrieves the data from Yahoo Finance and make no assumptions about the visualizations or analyses performed with these financial data. Consequently, `financr` dependencies are kept low.

Other R packages retrieves data from the same source as `'financr'`, i.e. Yahoo Finance. E.g., [`'yahoofinancer'`](https://cran.r-project.org/package=yahoofinancer), [`'quantmod'`](https://cran.r-project.org/package=quantmod) and the packages that depends on them such as [`yfr`](https://cran.r-project.org/package=yfR) and [`stocks`](https://cran.r-project.org/package=stocks) (depends on `'quantmod'`). 

Regarding the fetching of historical financial values from Yahoo Finance, the returned objects of these packages have different properties, see below. 

```{r echo=FALSE}

deps <- data.frame(Package = c("`'financr'`", "`'yahoofinancer'`"
                               , '`yfr`'
                               , "`'quantmod'`")
  
, get_historic = c("`financr::get_historic()` return a standard `data.frame`" 
               ,  "`'yahoofinancer'` methods return an `'R6'` class object (e.g., `Ticker$get_history`)"
              ,  '`yfr::yf_get()` return a tibble' 
                 , "`getSymbols()` from the `'quantmod'` package return a time series object (`'xts'` & `'zoo'` object)" ) )

knitr::kable(deps, row.names = F, caption = "Table 2. `'financr'` `get_historic()` Alternatives and Returned Values")


```


Other functions offered by these packages are sometimes more or less equivalent (e.g., `financr::valid_symbol()`) whereas other functions are specific to one of these packages. E.g., `'financr'` offer free-text search with `financr::get_info_from_name()`, while `'quantmod'` offers financial data-analysis oriented functions and time series data visualization methods. Other packages are derivated from these 2 examples, e.g.,  which rely on quantmod and ans.

