---
title: "Get_changes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get_changes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This vignette is about using `financr` functions to understand and exchange currencies, from financial currencies symbols. 

**get_changes() & get_changes_historic()**

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

- `financr::get_changes()` compute changes with the latest exchange rate, given currencies symbols.

```{r changes}
library(financr)

changes <- get_changes(from = c("RON", "USD"), to = "EUR")

# print the exchange rate :
head(changes[ , c("from", "to",  "regularmarketprice", "currency", "timestamp")])

```


- `financr::get_changes_historic()` return a `data.frame` with the historic of exchange rates, given currencies symbols. In addition of these historical values, the attributes of this `data.frame` have the latest exchange rates returned by `financr::get_changes()`.

```{r change-historic}

changes <- get_changes_historic(from = c("EUR", "RON") )

# Historic of exchange rate (2 first lines) 
head(changes, 2)

```

---
**get_currencies()** 

- `financr::get_currencies()` return a list of currencies symbols and names. This is helpful to understand the currencies symbols of the Yahoo Finance API, such as the `currency` column of the `data.frame` returned by `financr::get_historic`. 

```{r currencies}
# If you need to understand a currency symbol
currencies <- get_currencies()
str(currencies)
# If you need to understand a currency symbol :

few_currencies <- get_currencies(keep = c("RON",  "USD") )
few_currencies

```


<!-- --- -->
<!-- **Technical details.** `financr::get_changes()` behavior is similar to `paste(from, to, "-X")`. Thus : -->

<!-- - it's fine to convert several value into *one* other values, and vice-versa ; -->
<!-- - it's fine to convert a list of paired values ; -->
<!-- - 2 list of different lengths will lead to messy results. -->
