---
title: "get_info_and_historic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_info_and_historic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette show how to fetch data from company names and get historic financial data from Yahoo API.


**Search for ticker symbols, given keyword(s).**

```{r setup}
library(financr)
# Search symbols of all index with dow jones or euronex
indices <- search_from_text(texts = c("Dow jones", "euronext"), type = "index" )
str(indices)
```

**Search for symbols and latest prices on the exchange places, given keyword(s).**

```{r example-price}
# Search the symbols of volvo car and Saab in the Stockholm exchange place
swedish <- get_info_from_name(names = c("VOLVO car", "SAAB")
                         , exchange = "STO")
str(swedish)

```

**Get historical financial data, given symbols of assets.** 

```{r example3}
# Get historical values, given ticker symbol(s)
historic <- get_historic(symbols = swedish$symbol)

str(historic)
```

Additional attributes indicates such as the symbols of currencies in the `data.frame`, e.g., attributes of the `'finance'` `data.frame` from the previous example indicates that prices are in the 'SEK' currency. 

**Find names of all currencies with `financr::get_currencies()`.**
 
```{r}
unknown_currencies <- unique(historic$currency)

explaination <- get_currencies(unknown_currencies)

head(explaination)

```

See how to convert it to another currency such as 'USD' with the [Vignette of `get_changes()` and `get_currencies()`](https://clement-lvd.github.io/financr/articles/Get_changes.html). 

