---
title: "get_info_and_historic"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{get_info_and_historic}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette show how to fetch data from company names and get historic financial data from Yahoo API.

```{r setup}
library(financr)
```

Fetch ticker symbols associated with keyword(s) such as companies names, and get historical financial data for these symbols. 

```{r example3}
# 1) fetch_indices (optionally filter a precise marketplace)
indices <- get_info_from_name(names = c("VOLVO", "RENAULT")
                         , exchange = "STO")
# Keep only the swedish exchange place (STOckholm)

# 2) Fetch historical values, given ticker symbol(s)
datas <- get_historic(symbols = indices$symbol)

str(datas)
```

If you need to, see what are these currencies with `financr::get_currencies()`.
 
```{r}

unknown_currencies <- unique(datas$currency)

explaination <- get_currencies(unknown_currencies)

head(explaination)

```

See how to convert it to another currency such as 'USD' with the [Vignette of `get_changes()` and `get_currencies()`](https://clement-lvd.github.io/financr/articles/Get_changes.html). 

