---
title: "The 'last_' family of functions"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{The 'last_' family of functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette is about the functions with the prefix '`last_`'.

### Fetching the API
Retrieve market summary insights.

```{r}
library(financr)

datas <- last_market_summary(region = "US")

str(datas)

```

Or retrieve currencies and their latest 'USD' values, e.g. currencies with a 3-letters ISO code that begin with 'Z'.
 
```{r}

last_currencies(keep = "^Z", get_changes = T)

```


---

### Scraping on Yahoo Finance

Some functions rely on web scraping (Yahoo Finance webpages), such as `last_indices()` and `last_crypto()` which respectively provide the latest financial values (in USD) for over 40 global market indices and 100 cryptocurrencies.

`last_indices()` return a `data.frame` with the latest financial value of major world financial indices.

```{r indices}
indices <- last_indices()
str(indices)
```

---

`last_crypto()` return a `data.frame` of 100 crypto-currencies values in USD ($). 

```{r crypto}
krypt <- last_crypto()
str(krypt)
```

